Functional Enrichment Tests: Intro and methods comparison

### 2023-09-19 DRAFT_Funct_Enrich.Rmd
rm python path
updated python code for using annotation API

```{r, include=FALSE}
knitr::opts_chunk$set(engine.path = '/usr/bin/python3')

```{python}
uniprot-retrieval.py SPID.txt
```

```{r, engine.path = '/usr/bin/python3'}
uniprot-retrieval.py
```

>>>>

Instead of using the web interface, one can also use the API.

```{bash}
python3 DRAFT_Funct_Enrich/annot/uniprot-retrieval.py DRAFT_Funct_Enrich/annot/SPID.txt
```
